%				\begin{itemize}
%				\item \textbf{Time: }
%				\item \textbf{Act: }
%				\item \textbf{Response: }
%				\item	\textbf{Source: }
%				\end{itemize}


% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass[12pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
\usepackage{setspace}
\usepackage{parskip}
\parskip = 0.3 \baselineskip %\advance\parskip by 0pt plus 2pt% to change between paragraphs space
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

% \usepackage{gravarphicx} % support the \includegravarphics command and options
% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...
\usepackage[fleqn]{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{natbib}
\usepackage{blindtext}
\usepackage{titlesec}


%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}

%%% SECTION TITLE APPEARANCE
\usepackage{sectsty}
\allsectionsfont{\rmfamily\bfseries\upshape} % (See the fntguide.pdf for font help)
% (This matches ConTeXt defaults)

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

\usepackage[colorlinks,citecolor=black,urlcolor=black,bookmarks=false,hypertexnames=true]{hyperref} 
%%% END Article customizations



%%% The "real" document content comes below...

\title{RA Meeting Notes}
\author{Xing Mingjie}
\date{\today} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed 

\begin{document}
\maketitle

\tableofcontents

\newpage

\section{Dr.\ Xiaomei Sui}
	\subsection{23 Sept 2023}
		\begin{itemize}
		\item firm dynamics studies the hetero distributional effect of aggregate policy
		\item it uses structural models to explain mechanism and drives DID or other empirical methods
		\item productivity growth can be explained by:
			\begin{itemize}
			\item resource misallocation across firms
			\item exogenous frictions and/or technological change within firms
			\item globalization
			\item et cetera
			\end{itemize}
		\item dispute between US and China in trade and tech features bias on export and innovation policy.
		\item literature ignores heterogenous firms especially disaggregated firm/ sector behavior on the whole market as affected by the policy. We can conclude policy implications in terms of measures and timing from this study.
		\end{itemize}
	\subsection{05 Oct 2023}
		\begin{itemize}
		\item focus: CHIPs and Science Act; Plaza Accord; Innovation Act
		\item global value chain: new mechanism, new element. We use data (event study) and combine multi-country model to study policy instruments that protect domestic innovation.
		\item priority is on paper summary
		\item literature focus more on tariff and export ban, but few on innovation and regional cooperation and competition. trade literature features welfare gains and comparative advantage.
		\item we study nation's means of competition.
		\item framework
			\begin{itemize}
			\item trade
			\item FDI/ Innovation
				\begin{itemize}
				\item Time
				\item Target (Region, sector, firm)
				\item Act (Subsidy, Ban, Tax)
				\item Note: focus is on impact.
				\end{itemize}
			\end{itemize}
		\end{itemize}
	\subsection{2 Nov 2023}
		\begin{itemize}
		\item create own list matching ISO code, country name from WB etc.
		\item policy change over time. search firm sector country for counterfactual.
		\end{itemize}
	\subsection{16 Nov 2023}
		\begin{itemize}
			\item Communication between academics: reduced form knowledge spillover = 0. search and matching. random meeting. worker probability meet and communicate and thus knowledge diffusion. reduced prob of meeting.
			\item Marta Prato 2022
			\item caliendo: diffusion with goods/ workes(deciding place to work. the measure of diffusion)
			\item First try a small dataset: first make sure it works.
			\item model to solve lack of causality. change para: change force: result ----clear causality.
			\item melitz hopenhayn kelette kortum
		\end{itemize}
	\subsection{6 Dec 2023}
		\begin{itemize}
			\item 5-year growth, 3-year growth rate to check growth implications
			\item customer base model: firm invest in ad and amrketing to acquire new customers thereby shift demand
			\item markup model: firms accumulate reputation/ market power and charge for higher markups
			\item Herfindahl-Hirschman Index (HHI) is a common measure of market concentration and is used to determine market competitiveness, often pre- and post-merger and acquisition (M\&A) transactions.
			\item TFPR vs TFPQ
			\item entry margin
			\item exit margin for India, high exit barrier
			\item quant analysis, specific about key parameters to calibrate, to know what is missing in literature
			\item entry regulation literature. entrance can have direct hetero among entrants, regulations to support entrants with higher potential. deregulation grows entry.
		\end{itemize}
		
	\subsection{7 Dec 2023}
		\begin{itemize}
			\item sales growth  calculation
			\item generic programming
			\item two models
			\item how data goes
			\item convergence formula of rodrik2016
		\end{itemize}
\newpage

\footnotesize
\bibliographystyle{apalike}
\bibliography{RA_Meeting_Notes}

\end{document}